Specifying and Verifying the Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
Remove Doxygen FORD integration feature (space constraints)
lightweight subsumes abstract

% Emphasis here is on documentation generation, so it makes little sense to
% compare this aspect of CamFort to ad hoc testing. Apples and oranges.
\item A specification concisely captures the access pattern of a
  stencil and turns it into documentation. The inference procedure
  efficiently produces specifications with no programmer intervention,
  automatically inserting specifications at appropriate places in the
  source code.
%
\item Specifications are integrated into the code as comments for easy
  integration with existing tools, as well as documentation systems (\eg{}, we
  support Doxygen and FORD syntax).
%
\item Our specification format is deliberately abstract, with a small number of
  combinators that \emph{do not involve any indexing expressions}, \eg{}
  \texttt{a(i+1,j-1)}. This contrasts with other specification approaches. If a
  user specifies, say, the Naiver-Stokes stencil above, in a deductive
  verification language such as ACSL, they must write a specification involving
  textually dense array-indexing expressions. Therefore, any low-level mistakes
  that could be made whilst programming complex indexing code could also be
  made when writing its specification. Our specifications are more abstract and
  lightweight with the aim of aiding adoption by scientists and preventing
  indexing errors.
\end{itemize}

>>>>

% Emphasis here is on documentation generation, so it makes little sense to
% compare this aspect of CamFort to ad hoc testing. Apples and oranges.
\item A specification concisely captures the access pattern of a
  stencil and turns it into documentation. The inference procedure
  efficiently produces specifications with no programmer intervention,
  automatically inserting specifications at appropriate places in the
  source code.
%
%\item Specifications are integrated into the code as comments for easy
%  integration with existing tools, as well as documentation systems (\eg{}, we
%  support Doxygen and FORD syntax).
%
\item Our specification format is deliberately abstract, with a small number of
  combinators that \emph{do not involve any indexing expressions}, \eg{}
  \texttt{a(i+1,j-1)}. This contrasts with other specification approaches. If a
  user specifies, say, the Naiver-Stokes stencil above, in a deductive
  verification language such as ACSL, they must write a specification involving
  textually dense array-indexing expressions. Therefore, any low-level mistakes
  that could be made whilst programming complex indexing code could also be
  made when writing its specification. Our specifications are more lightweight
  with the aim of aiding adoption by scientists and preventing indexing errors.
\end{itemize}
